Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-16 doc/manuscript/ESSDmanuscript.Rmd
describe new or modified fields

n_new_variables = 11 + 2 + 2 #delta. + woody.mortality + O horizon
```

@@

Previous versions of ForC [@refs] contained most of the information required for transfer to EFDB, and, more broadly, to inform C accounting under IPCC guidelines. 
However, modest changes to the structure and contents of ForC were needed in order to provide all information required by EFDB and to improve ForC's capacity to serve as a repository of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of the ForC database, we added or modified ## fields (`r table_ForCchanges`), defined `r n_new_variables` new variables, implemented enhanced quality control, manually reviewed ># records to obtain additional required information, and added # new records.

@@

(`r table_ForCchanges`)

@@

# ForC to EFDB data transfer

>>>>

n_new_variables = 11 + 2 + 2 #delta. + woody.mortality + O horizon
# get n fields modified
sampling_details <- read.csv(paste0(path_to_ForC,"/ForC/database_management_records/record_of_changes.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_fields_modified =  length(sampling_details[,"Column"]) + 4 
```

@@

Previous versions of ForC [@refs] contained most of the information required by EFDB, and, more broadly, to inform C accounting under IPCC guidelines. 
However, modest changes to the structure and contents of ForC were needed in order to provide all information required by EFDB and to improve ForC's capacity to serve as a repository of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of the ForC database, we added or modified `r n_fields_modified` fields (`r table_ForCchanges`), defined `r n_new_variables` new variables, implemented enhanced quality control, manually reviewed ># records to obtain additional required information, and added # new records.

@@

We added or modified a total of `r n_fields_modified` fields (`r table_ForCchanges`).
Most notably, these included improvement of the representation of uncertainty, recording of original units and organic matter to C conversion factors, and expanding the information recorded in the citations table. 
For the latter, we *used an R script to automatically retrieve information based on the DOI*<!--needs info from Valentine here-->.

@@

# Transfer of data from ForC to EFDB

### 2022-04-16 doc/manuscript/ESSDmanuscript.tex
describe new or modified fields

Previous versions of ForC \citep{refs} contained most of the information
required for transfer to EFDB, and, more broadly, to inform C accounting
under IPCC guidelines. However, modest changes to the structure and
contents of ForC were needed in order to provide all information
required by EFDB and to improve ForC's capacity to serve as a repository
of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of
the ForC database, we added or modified \#\# fields (Appendix A),
defined 15 new variables, implemented enhanced quality control, manually
reviewed \textgreater\# records to obtain additional required
information, and added \# new records.

@@

(Appendix A)

@@

\section{ForC to EFDB data transfer}

>>>>

Previous versions of ForC \citep{refs} contained most of the information
required by EFDB, and, more broadly, to inform C accounting under IPCC
guidelines. However, modest changes to the structure and contents of
ForC were needed in order to provide all information required by EFDB
and to improve ForC's capacity to serve as a repository of valuable
information for forest C accounting under IPCC guidelines. To support
export of data to EFDB, and to improve the overall quality of the ForC
database, we added or modified 18 fields (Appendix A), defined 15 new
variables, implemented enhanced quality control, manually reviewed
\textgreater\# records to obtain additional required information, and
added \# new records.

@@

We added or modified a total of 18 fields (Appendix A). Most notably,
these included improvement of the representation of uncertainty,
recording of original units and organic matter to C conversion factors,
and expanding the information recorded in the citations table. For the
latter, we \emph{used an R script to automatically retrieve information
based on the DOI}.

@@

\section{Transfer of data from ForC to EFDB}
